### 2017-05-31 doc/response.tex

\newpage
\pagenumbering{roman}

\noindent
Dear Dr.~Merlo,
\newline

Thank you for the very helpful suggestions and insightful questions
posed in this review.  We apologize for the delay getting this
revision back to you and very much appreciate the extension you 
gave us to resubmit the manuscript.

We have substantially revised the article in response to yours and the reviewers' 
comments. Specifically with regard to the two main issues you raised, we have 
introduced a uni-modal language model (referred to as the {\sc LM} model in the text) 
and reported the results of all the experiments on this model as well. Also following 
your recommendation, we have removed the exploratory parts of (the old) Section 6, 
and reorganized the paper by merging previous Sections 4, 5 and the remaining of 
Section 6 into a single section (Section 4 in the revised manuscript) reporting all the 
experiments. We have kept and expanded the quantitative analysis of the nature of 
n-gram contexts that trigger individual dimensions in the hidden layers; this experiment is now reported in Section~\ref{sec:contexts}.

Furthermore, we have made clarifications about the details of the techniques all 
through the manuscript, expanded Introduction (Section~\ref{sec:intro}) to 
emphasise our contributions, updated Related Work (Section~\ref{sec:related}) 
to include relevant papers that came out while this manuscript was under review, and expanded the Discussion

\todo[inline]{explain the major revisions}

### 2017-05-31 doc/response.tex

\newpage
\pagenumbering{roman}

\noindent
Dear Dr.~Merlo,
\newline

Thank you for the very helpful suggestions and insightful questions
posed in this review.  We apologize for the delay getting this
revision back to you and very much appreciate the extension you 
gave us to resubmit the manuscript.

We have substantially revised the article in response to your and the reviewers' 
comments. Specifically with regard to the two main issues you raised, we have 
introduced a uni-modal language model (referred to as the {\sc LM} model in the text) 
and reported the results of all the experiments on this model as well. Also following 
your recommendation, we have removed the exploratory parts of (the old) Section 6, 
and reorganized the paper by merging previous Sections 4, 5 and the remaining of 
Section 6 into a single section (Section 4 in the revised manuscript) containing all the 
experiments. We have kept and expanded the quantitative analysis of the nature of 
n-gram contexts that trigger individual dimensions in the hidden layers; this experiment is now reported in Section~\ref{sec:contexts}.

Furthermore, we have made clarifications about the details of the techniques all 
through the manuscript, expanded Introduction (Section~\ref{sec:intro}) to 
emphasise our contributions, updated Related Work (Section~\ref{sec:related}) 
to include relevant papers that came out while this manuscript was under review, and expanded the Discussion to discuss in more detail the relevance and generalizability of our techniques.

### 2017-05-31 doc/response.tex

- In section 6.1, why is the sorting by magnitude and not by absolute
  value? are negative activations not important?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  It is in fact the absolute value of the activations 
that is taken into account. We have changed the description of the top-k-contexts 
method to clear this issue.
\end{quote}
\begin{verbatim}

- When choosing the "top k context of each unit" (section 6.1), it is
  not clear what a "unit" is and how it is chosen.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  A unit is one neuron in the final hidden layer 
of the network. We have made this clear in the revised text.
\end{quote}
\begin{verbatim}

- I did not understand the last sentence in section 6.1, and would
  appreciate an elaboration on this point (or a removal).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We removed that sentence and added an expanded discussion of the generalizability of our techniques to the last section.
\end{quote}
\begin{verbatim}

- In section 6.2, it is not clear how trigrams with high activations
  are chosen. How is a trigram with high activation defined? this is
  not clear from the description of the method.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We removed this section in the revised manuscript. We address the nature of contexts which trigger individual dimensions in more detail now in Section~\ref{sec:contexts}.
\end{quote}
\begin{verbatim}

@@

Revisions to be Required:
: 
- clearer description of how top k contexts are obtained
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As mentioned above, we have rewritten Section~\ref{sec:micro} to make the description of the methods and the experiments more clear.
\end{quote}
\begin{verbatim}

Revisions to be Encouraged:
: 
- figures are not readable in BW printing; in addition to color, use
  different symbols/line types
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{update graphs?}
\end{quote}
\begin{verbatim}

- Related Work: clarify better how you differ from Li et al. (2015),
  you mention "for a comparative analysis": I interpret this as "we
  analyze a multi-task learning model (visual / textual) and compare
  what the two parts learn"
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have edited our related work section to make the comparison more 
clear. In addition to taking into account tasks that rely on different modalities (language as well as vision), 
we focus more on learning structural properties of the input, whereas Li et al. (2015) focus on single
tokens.
\end{quote}
\begin{verbatim}

5 Minor Revisions Required [Help]
: 
- Sec 2, clarify: what are 'negative strings'? (non-words?)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  we have reworded `positive' and `negative' as `grammatical' 
and `ungrammatical' to avoid confusion.
\end{quote}
\begin{verbatim}
- Before equation 9 missing lambda ("weighted by \lambda"; what lambda
  is used in the exp.?)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  There was no $\lambda$ in that equation, but in 
Section{sec:imaginer} we now report the value we use for the parameter 
$\alpha$ in Equation~(\ref{eq:losscombo}).
\end{quote}
\begin{verbatim}
- it would be helpful to include a figure of model (as in original
  paper)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have included an illustration of the structure of the model in Figure~\ref{fig:imaginet}.
\end{quote}
\begin{verbatim}
- "two minor modifications" but the first seems you also use cosine,
  was that different previously, not clear.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  You are right, the description of the model in Section~\ref{sec:imaginet} presents the version used in this paper, which uses cosine distance. The original Imaginet model uses mean square error instead; we clarified this issue in footnote~\ref{ft:imaginet}.  
\end{quote}
\begin{verbatim}
- specify interaction features in regression model
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have specified the interaction features used in each regression model in Section~\ref{sec:beyond lexical}.
\end{quote}
\begin{verbatim}
- 5.3.1. why also 'water'?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have removed the {\it water} from the set of examples in Figure~\ref{fig:top_words}.
\end{quote}
\begin{verbatim}

@@

Strengths:
: 
This paper makes a useful methodological contribution by proposing
methods to analyze the knowledge learned by neural networks, which is
an underexplored area, at least for networks trained on text data. The
paper is well written, and technically sound.

Weaknesses:
: 
The results of the paper are unfortunately fairly obvious. From the
omission score analysis, we learn that a model trained to predict the
next word in a sentence is sensitive to function words, while a word
trained to associate a sentence with an image representation (which is
essentially the output of the object detector) pays more attention to
nouns. This is not at all surprising, it just reflects the different
training objectives. The fact that the hidden units respond to
specific n-grams is also expected; most people already believe that
RNNs are good at approximating n-gram models; the question is, can
they model more elaborate syntactic structures?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address}
\end{quote}
\begin{verbatim}

This is really the question that the authors should explore, e.g., by
testing whether the model can learn long distance dependencies,
agreement, recursion, word order. An example for recent work that goes
in this direction is Linzen et al. (2016).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have expanded the related work 
(Section~\ref{sec:related}) with a discussion of Linzen et al. (2016) 
and a few other articles that came out while our submission was under review.
\end{quote}
\begin{verbatim}

Another limitation of the paper is its focus on one particular model,
which happens to be the authors'. To be convincing, the paper would
really need to compare results for this model with results for other
architectures, showing that the proposed analysis methods offer real
discriminative power.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Due to space and time limitations we have to 
leave the comparison with other architectures for future work; however we 
have added a section to Discussion to discuss the generalizability of our 
techniques to other architectures in more detail.
\end{quote}
\begin{verbatim}

@@

Related to this, it is not clear to me why a multimodal, multitask
model such as Imaginet is required for the work presented
here. Surely, similar results would be obtained if two unimodal RNN
models were trained, one on image descriptions to predict the next
word, and one on image representations to predict the description.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address}
\end{quote}
\begin{verbatim}

4 Substantive Revisions Required [Help]

Complete this section if either 'Revise and Resubmit' or 'Reject' has
been recommended.

Revisions to be Required:
: 
(1) Add comparisons to unimodal models (or at least to unimodal
versions of Imaginet).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  In the revised manuscript we have introduced a uni-modal language model, and updated all are experiments to include this model as well.
\end{quote}
\begin{verbatim}

(2) Add comparisons to other architectures (LSTMs, etc.)
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  As we mentioned before, we are very interested in 
applying our proposed techniques to other tasks and architectures in future work. 
For the sake of this manuscript, we have included a theoretical discussion of how these techniques can be implemented for a number of other architectures.
\end{quote}
\begin{verbatim}

(3) Sec. 5.3.2 should be cut. You don't have connected discourse, just
isolated sentences. So it is purely speculative to say these
observations are due to topic/content structure, rather than just to
linear order.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Our explanation of the aim of this experiment in the original version might have been misleading; we have rewritten this section to make it clear that we are examining the information structure within a single sentence and not in a dialogue. We do believe that the results we report in this section are interesting and nontrivial, especially the fact that the position usually occupied by the subject of the sentence is the most important for the {\sc Visual} model despite the common recency bias in RNNs.
\end{quote}
\begin{verbatim}

(4) The paper relies too much on impressionistic evaluation based on
suggestive figures, rather than on quantitative analysis. An exception
is Fig. 8. There should be more of this type of analysis.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  We have removed the exploratory parts of (the old) Section 6, and expanded the quantitative analysis of the nature of triggering contexts in Section~\ref{sec:contexts}. 
\end{quote}
\begin{verbatim}

### 2017-05-31 doc/models.tex
response letter updated

Formally, each sentence is mapped to two sequences of hidden states, 
one by {\sc Visual} and the other by {\sc Textual}:
\vspace{-.2cm}
\begin{align}
  \mathbf{h}^{V}_t = \mathrm{GRU}^V(\mathbf{h}^{V}_{t-1},\mathbf{x}_t)\\
  \mathbf{h}^{T}_t = \mathrm{GRU}^T(\mathbf{h}^{T}_{t-1},\mathbf{x}_t)
\vspace{-.1cm}
\end{align}
%
At each time step {\sc Textual} predicts the next word in the sentence
$S$ from its current hidden state $\mathbf{h}^{T}_t$, while {\sc
  Visual} predicts the image-vector\footnote{Representing the full image, 
  extracted from the pre-trained Convolutional Neural Network of 
  \namecite{simonyan2014very}. \label{edit:dumdumeddy}}
$\hat{\mathbf{i}}$ from its last
hidden representation $\mathbf{h}^{V}_t$.
%
\vspace{-.2cm}
\begin{align}
   \hat{\mathbf{i}} &= \mathbf{V} \mathbf{h}^{V}_\tau \\
    p(S_{t+1}|S_{1:t}) &= \mathrm{softmax}(\mathbf{L}\mathbf{h}^T_t)
\vspace{-.1cm}
\end{align}
%
The loss function is a multi-task objective which penalizes error on
the visual and the textual targets simultaneously. The objective
combines cross-entropy loss $L^{T}$ for the word predictions
and cosine distance $L^V$ for the image
predictions\footnote{Note that the original formulation in
  \namecite{chrupala2015learning} uses mean squared error instead; as the performance of
{\sc Visual} is measured on image-retrieval which is based on cosine 
distances, we use cosine distance as the visual loss here.}, weighting them with the parameter $\alpha$ (set to $0.1$).
%
%\vspace{-.2cm}
\begin{align}
%\begin{equation}
%\label{eq:lossce}
&L^{T}(\theta) = {-} \frac{1}{\tau}\sum_{t=1}^\tau \log p(S_t|S_{1:t}) \\
%\end{equation}
%
%\vspace{-.2cm}
%\begin{equation}
%\label{eq:losscos}
&L^V(\theta) =  1 - \frac{\hat{\mathbf{i}} \cdot \mathbf{i}}{\| \hat{\mathbf{i}} \| \| \mathbf{i} \|} \\
%\end{equation}
%
%\vspace{-.2cm}
%\begin{equation}
%\label{eq:losscombo}
&L = \alpha L^T + (1-\alpha)L^{V}
\end{align}
%L^V(\theta) &= \frac{1}{K}\sum_{k=1}^K(\hat{i}_k-i_k)^2
%

>>>>

Formally, each sentence is mapped to two sequences of hidden states, 
one by {\sc Visual} and the other by {\sc Textual}:
\vspace{-.2cm}
\begin{align}
  \mathbf{h}^{V}_t = \mathrm{GRU}^V(\mathbf{h}^{V}_{t-1},\mathbf{x}_t)\\
  \mathbf{h}^{T}_t = \mathrm{GRU}^T(\mathbf{h}^{T}_{t-1},\mathbf{x}_t)
\vspace{-.1cm}
\end{align}
%
At each time step {\sc Textual} predicts the next word in the sentence
$S$ from its current hidden state $\mathbf{h}^{T}_t$, while {\sc
  Visual} predicts the image-vector\footnote{Representing the full image, 
  extracted from the pre-trained Convolutional Neural Network of 
  \namecite{simonyan2014very}. \label{edit:dumdumeddy}}
$\hat{\mathbf{i}}$ from its last
hidden representation $\mathbf{h}^{V}_t$.
%
\vspace{-.2cm}
\begin{align}
   \hat{\mathbf{i}} &= \mathbf{V} \mathbf{h}^{V}_\tau \\
    p(S_{t+1}|S_{1:t}) &= \mathrm{softmax}(\mathbf{L}\mathbf{h}^T_t)
\vspace{-.1cm}
\end{align}
%
The loss function is a multi-task objective which penalizes error on
the visual and the textual targets simultaneously. The objective
combines cross-entropy loss $L^{T}$ for the word predictions
and cosine distance $L^V$ for the image
predictions\footnote{Note that the original formulation in
  \namecite{chrupala2015learning} uses mean squared error instead; as the performance of
{\sc Visual} is measured on image-retrieval which is based on cosine 
distances, we use cosine distance as the visual loss here.\label{ft:imaginet}}, weighting them with the parameter $\alpha$ (set to $0.1$).
%
%\vspace{-.2cm}
\begin{align}
%\begin{equation}
%\label{eq:lossce}
&L^{T}(\theta) = {-} \frac{1}{\tau}\sum_{t=1}^\tau \log p(S_t|S_{1:t}) \\
%\end{equation}
%
%\vspace{-.2cm}
%\begin{equation}
%\label{eq:losscos}
&L^V(\theta) =  1 - \frac{\hat{\mathbf{i}} \cdot \mathbf{i}}{\| \hat{\mathbf{i}} \| \| \mathbf{i} \|} \\
%\end{equation}
%
%\vspace{-.2cm}
%\begin{equation}
\label{eq:losscombo}
&L = \alpha L^T + (1-\alpha)L^{V}
\end{align}
%L^V(\theta) &= \frac{1}{K}\sum_{k=1}^K(\hat{i}_k-i_k)^2
%
